
```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest) # to scrape wikipedia page
```

# Where Do People Drink The Most Beer, Wine And Spirits?

Back in 2014, [fivethiryeight.com](https://fivethirtyeight.com/features/dear-mona-followup-where-do-people-drink-the-most-beer-wine-and-spirits/) published an article on alchohol consumption in different countries. The data `drinks` is available as part of the `fivethirtyeight` package. Make sure you have installed the `fivethirtyeight` package before proceeding.


```{r, load_alcohol_data}
library(fivethirtyeight)
data(drinks)

# or download directly
# alcohol_direct <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/alcohol-consumption/drinks.csv")

```


```{r glimpse_skim_data}
glimpse(drinks)
```

Plot showing the top 25 beer consuming countries

```{r beer_plot}
drinks %>% 
  slice_max(order_by = beer_servings, n=25) %>% 
  ggplot(aes(x = beer_servings, y = fct_reorder(country, beer_servings))) +
  geom_col() +
  labs(
    title = "Most Beer Drinking Countries",
    x = "Beer Servings",
    y = "Countries"
  )
```

Plot showing the top 25 wine consuming countries

```{r wine_plot}
drinks %>% 
  slice_max(order_by = wine_servings, n=25) %>% 
  ggplot(aes(x = wine_servings, y = fct_reorder(country, wine_servings))) +
  geom_col()+
  labs(
    title = "Most Wine Drinking Countries",
    x = "Wine Servings",
    y = "Countries"
  )
```

Plot showing the top 25 spirit consuming countries

```{r spirit_plot}
drinks %>% 
  slice_max(order_by = spirit_servings, n=25) %>% 
  ggplot(aes(x = spirit_servings, y = fct_reorder(country, spirit_servings))) +
  geom_col()+
  labs(
    title = "Most Spirit Drinking Countries",
    x = "Spirit Servings",
    y = "Countries"
  )
```

Key takeaways: 
Wine seems to be consumed mostly in Europe while both beer and spirit has higher spread throughout the world. Also, while both wine and beer follow a continuous decrease from most drinking country to least drinking, spirit seems to drop heavily after the two top most drinking countries which are Grenada and Belarus. This mean that Grenada and Belarus drink much more spirit than other most spirit drinking countries.
